Sequential rank agreement methods for comparison of ranked lists

### 2015-05-08 latex/paper.Rnw
Text update

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage[noae]{Sweave}
\usepackage{authblk}

%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

@@

The agreement, $A(X_p)$, cannot be computed directly for all
predictors because we only observe a censored version of $\tilde R$
for some of the lists. Instead we assume that the rank assigned to
item $X_p$ in list $l$ is uniformly distributed among the ranks that
have \emph{not} been assigned for list $l$, so the augmented agreement
becomes
\begin{equation}
\tilde A(X_p) = \frac{\sum_{r_1; r_1\in \tilde R_1(X_p)}  \cdots
  \sum_{r_L; r_L\in \tilde R_L(X_p)} A(X_p)}{\prod_l |\tilde
  R_l(X_p)|}. \label{formula:censored-agreement}
\end{equation}
Similarly, the sequential rank agreement becomes
\begin{equation}
XXX \textrm{SRA}(d)= \sqrt{\frac{\sum_{\{p \in S_d\}}(L-1)\tilde{A}(X_p)^2}{(L-1)|S_d|}}, \label{def:sra-censored}
\end{equation}

@@

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{calc}
\usepackage[noae]{Sweave}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}
%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

@@

The agreement, $A(X_p)$, cannot be computed directly for all
predictors because we only observe the censored version of $R(X_p)$
for some of the lists. Instead we assume that the rank assigned to
item $X_p$ in list $l$ is uniformly distributed among the ranks that
have \emph{not} been assigned for list $l$. The algorithm is described
in detail in Algorithm~\ref{sra-algorithm}.

%, so the augmented agreement
%becomes
%\begin{equation}
%\bar{A}(X_p) = \frac{\sum_{r_1; r_1\in \tilde R_1(X_p)}  \cdots
%  \sum_{r_L; r_L\in \tilde R_L(X_p)} A(X_p)}{\prod_l |\tilde
%  R_l(X_p)|}. \label{formula:censored-agreement}
%\end{equation}
%Similarly, the sequential rank agreement becomes
%\begin{equation}
%XXX \textrm{SRA}(d)= \sqrt{\frac{\sum_{\{p \in S_d\}}(L-1)\tilde{A}(X_p)^2}{(L-1)|S_d|}}, \label{def:sra-censored}
%\end{equation}

@@

\begin{algorithm}
\caption{Sequential rank agreement algorithm for censored lists}
\label{sra-algorithm}
\begin{algorithmic}[1]
\Procedure{Censored rank agreement}{}
\State Let $B$ be the number of permutations to use
\For{each $b \in B$}
\For{each censored list $l \in L$}
\State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-2cm}{Permute the unassigned ranks, $k_l+1, \ldots, P$ and assign
them randomly to the items \emph{not} found in the list, i.e.,
$\Lambda^\complement$, in order to fill out the lists.}
\EndFor
\State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-1cm}{Let sra($b$) be the sequential rank agreement computed from the
filled out lists.}
\EndFor
\State Return element-wise averages across all $B$ permutations of sra($b$).
\EndProcedure
\end{algorithmic}
\end{algorithm}
